IML Term project paper

### 2022-12-10 paper.rmd
Update paper.rmd

Notable benefits of the logistic regression model include %tähän pitää vielä kirjoittaa lisää

>>>>

Notable benefits of the logistic regression model include that as a discriminative model it eventually reaches a lower asymptotic variance than comparable generative models. On top of this, compared to for example comparable support vector classifiers, on average logistic regression models fare better under situations where the classes are not easily separable by explanatory variables.
